A Prediction and Analysis of the interplay between Students and Salary Prospects in the STEM Field

### 2024-01-30 doc/DataLiteracyStudentProject/paper.tex
Final Version [PDF]

Our research focus is to provide valuable insights
into how future salaries affect the decision-making of students when it comes to selecting
their major at the University of Tubingen. For this
purpose we explore the dynamic relationship between student enrollment, expected salaries, and
graduation rates. We are exploiting the Vector
Autoregressive model to demonstrate a reliable
forecasts for future STEM student numbers, underscoring the significant influence of projected
income on these predictions.
Furthermore, by manipulating the salary variable in our analysis, we observe a corresponding increase or decrease in the number of students.
This implies a sensitivity in enrollment trends to changes in expected salary, highlighting the potential impact of financial considerations on academic choices.

@@

\section{Introduction}\label{sec:intro}
In recent years, a growing number of high school graduates have chosen the path of higher education.
Science, technology, engineering, and mathematics, known as STEM, make up a large proportion of all students, although
this academic career is known for being one of the most demanding.
This paper aims to explore the potential influence of financial incentives, uncovering hidden relations.

>>>>

Our research focus is to provide valuable insights
into how future salaries affect the decision-making of students when it comes to selecting
their major at the University of Tübingen. For this
purpose we explore the dynamic relationship between student enrollment, expected salaries, and
graduation rates. We are exploiting the Vector
Autoregressive model to demonstrate a reliable
forecasts for future STEM student numbers, underscoring the significant influence of projected
income on these predictions.
Furthermore, by manipulating the salary variable in our analysis, we observe a corresponding increase or decrease in the number of students.
This implies a sensitivity in enrollment trends to changes in expected salary, highlighting the potential impact of financial considerations on academic choices.

@@

\section{Introduction}\label{sec:intro}
In recent years, a growing number of high school graduates have chosen the path of higher education, according to \href{https://de.statista.com/infografik/27761/anzahl-eingeschriebener-mint-studentinnen-an-deutschen-universitaeten-nach-jahr/#:~:text=Technische%20Studiengänge&text=Rund%2037%20Prozent%20der%20drei,%2C%20Naturwissenschaft%20und%20Technik%2C%20eingeschrieben.}{Statista}.
Science, technology, engineering, and mathematics, known as STEM, make up a large proportion of all students, although
this academic career is known for being one of the most demanding.
This paper aims to explore the potential influence of financial incentives, uncovering hidden relations.
